                    % 类型定义 10pt font 单页 信纸
\documentclass[10pt,oneside,letter,final]{article}

\usepackage{array, lipsum, bibentry}
\usepackage{calc}

                    % 版面定义
\usepackage[left=2.0cm,right=1.5cm,top=1.8cm,bottom=1.5cm,nofoot]{geometry}

\pagestyle{empty}   % 无页眉页脚
\linespread{0.9}    % 行距0.9倍
\parindent=0pt      % 缩进值为0

                    % 简历头部样式定义
\newcommand{\CVtitle}[4]{
    \makebox[\textwidth][c]{\bf\Huge #1}\\[1pt]
    \makebox[0.2\textwidth][l]{\footnotesize  #2}\hspace{-3pt}
    \makebox[0.6\textwidth][c]{\footnotesize  #3}\hspace{-3pt}
    \makebox[0.2\textwidth][r]{\footnotesize  #4}\\[-4pt]
    \rule[5pt]{\textwidth}{.5pt}
}

                    % 栏目样式定义
\newenvironment{CVsection}[1]{
    \hspace*{20pt}{\bf \Large #1}\\[-3pt]
    \rule[5pt]{\textwidth}{1pt}\\
}{
    \hspace{-10pt}\hfill\\[10pt]
}

                    % tabular格式控制定义
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{M}{p{0.6\textwidth}}
\newcolumntype{R}{p{0.18\textwidth}}
\newcolumntype{C}{p{0.8\textwidth}}

                    % tabular纵向分割线样式定义
\newcommand\VRule{\vrule width 0.5pt}

                    % Experance栏内部样式定义
\newenvironment{CVexperience}[3]{
    {\bf #1}, #2\hfill #3\\[2pt]
    \begin{itemize}
        \setlength{\parsep}{0pt}
        \setlength{\itemsep}{0pt}\vspace{-16pt}
}{
    \end{itemize}
}

                    % Experance栏内部样式定义
\newenvironment{CVproject}[2]{
    {\bf #1}\hfill #2\\[2pt]
    \begin{itemize}
        \setlength{\parsep}{0pt}
        \setlength{\itemsep}{0pt}\vspace{-16pt}
}{
    \end{itemize}
}

\begin{document}
                                % 输出简历头部
    \CVtitle{Zhuowei (Steven) Wang}
        {(919) 455-3067}
        {1220 University CT APT 203, Raleigh, NC 27606}
        {job@silverwzw.com}\\[10pt]
                                % 输出Education栏
    \begin{CVsection}{\Large E\large DUCATION}
                                % 输出Education栏具体内容
        \begin{tabular}{L!{\VRule}M R}
            2012--2014 & {\bf Master} in {\bf Computer Science}, NC State Univ. & GPA 3.71/4.0\\[3pt]
            2010--2012 & {\bf Master} in Operations Research, NC State Univ. & GPA 3.82/4.0 \\[3pt]
            2006--2010 & {\bf Bachelor} in Electronic Engineering, Zhejiang Univ., China & GPA 82/100
        \end{tabular}
    \end{CVsection}
                                % 输出Skills栏
    \begin{CVsection}{\Large S\large KILLS}
                                % 输出Skills栏具体内容
        \begin{tabular}{L!{\VRule}C}
            Proficient in   & C, Java, C++ and Javascript\\[3pt]
            Experienced     & bash script, Assembly, SQL, Matlab, ASP, VBA, HTML \\[3pt]
            work with       & mongoDB, MySQL, JQuery, Servlet, JSON, XML, RESTful, Ruby, Node.js, Go, \LaTeX \\[1.5pt]
                            & gdb, vim, make, git, Eclipse, Visual Studio, FUSE, IIS, OPNET, Wireshark, tcpdump \\[1.5pt]
                            & Amazon EC2, Google App Engine
        \end{tabular}
    \end{CVsection}
 				% 输出Projects栏
    \begin{CVsection}{\Large P\large ROJECTS}
        \begin{CVproject}{KabiFS - a Distributed File System with Git-like version control capability}{Present}
            \item a File System based on mongoDB with concurrenct read write support
            \item Git-like version control - discard changes, mount a previous version, even branching.
            \item Distributed, FUSE/HDFS interface, NFS protocol. Load balancing and Map-Reduce support.
        \end{CVproject}
        
        \begin{CVproject}{Scrawler - a Content-aware Crawler}{Fall 2013}
            \item a crawler that use Natrual Language Processing (NLP) module to improve the hit rate on certain topic.
            \item Use NLP module to understand web content, determine the context of a link and  assign priorities to links
            \item Crawler take advatages from NLP module feedback and fetch links according to priority.
        \end{CVproject}
        
        \begin{CVproject}{P\&D cracker - a spare time project to crack P\&D}{Spring 2013}
            \item Use pptpd, bind9 and GAE-Java to build a MITM attack environment
            \item backend in Java with Servlet and AJAX frontend.
            \item Puzzle and dragon is the most popular game in Apple app store and Google Play Market in 2013.
        \end{CVproject}
        
        \begin{CVproject}{OTHER PROJECTS}{}
            \item {\bf ICE9 compiler,} A toy compiler transform ICE9 to Tiny Machine code. Written in flex, bison and C++
            \item {\bf XINU Kernel Patch,} XINU Kernel patch, for better semaphores and proc scheduler. in C and Assembly
            \item {\bf Open Source Project Expertiza,} Contributs a patch for better graphic, in Javascript
            \item {\bf {Performance modeling and simulation for Markov Service System}}
        \end{CVproject}
    \end{CVsection}
    \\[-20pt]                                % 输出Experience栏
    \begin{CVsection}{\Large E\large XPERIENCE}
                                %输出第一项Experience
        \begin{CVexperience}{Research Assistant}{Computer Science Dept., NC State Univ.}{Present}
                                %输出第二项Experience具体内容
            \item in the field of File System and Natural Language Processing
            \item Developed a Content-aware Crawler based on Java, MySQL and GATE (an NLP library)
            \item Currently working on a Distributed, Git-like (with Version Control) File System based on mongoDB 
        \end{CVexperience}
                                %输出第二项Experience
        \begin{CVexperience}{Cluster Operation \& Maintenance Intern}{Center for Innovation Management Studies}{Present}
                                %输出第一项Experience具体内容
            \item on IBM PPC and RHEL x86 clusters - Bash develop, Linux maintenance and operating, device installation.
            \item IBM Software Support: Deploy, migration and maintenance for IBM BigInsight and Content Analysis Sys.
        \end{CVexperience}
        
        \begin{CVexperience}{Web Developer Intern}{Zhejiang Univ.}{2006-2008}
            \item Designed and implemented a web system for news publishing, peer reviewing, member and activity management.
            \item maintenance to the Undergraduate Campus CMS web system.
        \end{CVexperience}
    \end{CVsection}
    \\[-20pt]
    \begin{CVsection}{\Large H\large ONORS}
        Outstanding Acadamic Performance Award,\quad Outstanding Undergraduate Student Award\hfill (Zhejiang Univ.)
    \end{CVsection}
\end{document}
